Deep Reinforcement Learning for Conservation Decisions

### 2021-08-17 manuscript/manuscript.Rmd
Added paragraph on scaling up to large problems

>>>>

<!-- Where/how to use deep RL -->
Yet, a more immediate barrier to deep RL being used in conservation is deep RL's hardware requirements.
Depending on the complexity of the RL environment and agent, the equipment necessary to train an agent can vary widely.
The examples shown above were selected so they can be replicated on a personal computer, but more realistic problems will likely require specialized computational resources.
For instance, one of the most notable achievements in RL, Alphastar, required 33 TPUs, processors that are specialized for deep learning, for more than 40 days [@alphastar].
Fully detailed conservation decision-making problems will likely require comparable specialized algorithms and hardware that ecologists do not generally have access to.
For deep RL to be an effective tool for conservation, there will need to be large investments of time and money, and extensive collaboration across computer science and ecology.
